Using CopyKAT to idenfity tumor cells in Ewing sarcoma samples

### 2024-05-17 analyses/cell-type-ewings/template_notebooks/03-copykat.Rmd

```{r}
# for every cell, calculate the mean detection level across all genes in a given chromosome
full_cnv_df <- full_ck_results_df |> 
  tidyr::pivot_longer(cols = -c(
    reference_used,
    abspos, 
    chromosome_name, 
    start_position, 
    end_position, 
    ensembl_gene_id, 
    hgnc_symbol, 
    band),
    names_to = "barcodes",
    values_to = "cnv_detection") |> 
  dplyr::group_by(chromosome_name, barcodes, reference_used) |> 
  dplyr::summarise(mean_cnv_detection = mean(cnv_detection))

# join with cnv info
cnv_df <- cnv_df |> 
  dplyr::left_join(full_cnv_df, by = c("barcodes", "reference_used"))
```

>>>>

```{r}
# for every cell, calculate the mean detection level across all genes in a given chromosome
full_cnv_df <- full_ck_results_df |> 
  tidyr::pivot_longer(cols = -c(
    reference_used,
    chrom
    ),
    names_to = "barcodes",
    values_to = "cnv_detection") |> 
  dplyr::group_by(chrom, barcodes, reference_used) |> 
  dplyr::summarise(mean_cnv_detection = mean(cnv_detection))

# join with cnv info
cnv_df <- cnv_df |> 
  dplyr::left_join(full_cnv_df, by = c("barcodes", "reference_used")) |> 
  dplyr::filter(!is.na(chrom))
```
